shrimp_goby_boatnoise

### 2025-02-20 ms_boatnoise_shrimp_goby.Rmd
Included a line to install cmdstanR for interfacing between brms and stan

```{r, message=FALSE, results='hide'}
#install.packages("pacman")
#require("pacman") 
pacman::p_load(tidyverse, ggplot2, brms, cmdstanr, broom, broom.mixed, tidybayes, ggthemes, emmeans, ggdist, gridExtra, bayesplot, see, patchwork, ggtext, extraDistr, gghalves, ggpp, rstan, gt)

>>>>

```{r, message=FALSE, results='hide'}
#install.packages("pacman")
#install.packages("cmdstanr", repos = c('https://stan-dev.r-universe.dev', getOption("repos")))
#require("pacman") 
pacman::p_load(tidyverse, ggplot2, brms, cmdstanr, broom, broom.mixed, tidybayes, ggthemes, emmeans, ggdist, gridExtra, bayesplot, see, patchwork, ggtext, extraDistr, gghalves, ggpp, rstan, gt)
